\texttt{ensmallen}: a flexible C++ library for efficient function optimization

### 2018-10-16 doc/mlsys_paper/paper.tex
Section 2 minor updates.

{\tt ensmallen} provides a {\bf set of optimizers} for
optimizing {\bf user-defined objective functions}.  It is also easy to implement a
new optimizer in the {\tt ensmallen} framework.  Overall, our goal is to provide
an easy-to-use library that can solve the problem
%\vspace*{-0.4em}
%\begin{equation}
$\operatorname{argmin}_{x} f(x)$
%\end{equation}
%\vspace*{-0.4em}
%\noindent
for any function $f(x)$ that takes a vector or matrix input $x$.  Ideally,
the user should only need to specify what $f(x)$ is, or provide an
implementation of a function that can compute $f(x)$.  However, it is very difficult to
implement something that is both generic and fast---for instance, gradient-based
approaches typically converge far quicker than gradient-free approaches.
As such, we must design an abstraction that is able to simultaneously generalize to
many problem types, as well as take advantage of accelerations and
code optimizations.
%% CS: in the above sentence, it's not clear what is meant by "we must design ..."
%% CS: should it be "we provide ..." or "ensmallen provides ..." ?
%% CS: The overall intent of the sentence is not clear -- to my eyes
%% CS: it doesn't seem to gel well with its surrounding context.

@@

To accomplish the flexibility, {\tt ensmallen} makes heavy use of
C++ template metaprogramming.
When implementing an objective function to be optimized,
a user can implement only a few methods; metaprogramming is then automatically
used to check that the given functions match the requirements of the
optimizer that is being used.  When implementing an optimizer, we can assume
that the given function to be optimized meets the required assumptions of the
optimizers, and encode those requirements as compile-time checks
(via \texttt{static\_assert}).

@@

The required API for separable differentiable objective functions (ie., those
that would use an optimizer like SGD) is very similar, except that
\texttt{Evaluate()}, \texttt{Gradient()} and \texttt{EvaluateWithGradient()}
should operate only on mini-batches.  The same pattern applies for other
types of objective functions: only a few methods specific to class of objective
function itself must be implemented and then any optimizer may be used.

>>>>

{\tt ensmallen} provides a {\bf set of optimizers} for
optimizing {\bf user-defined objective functions}.  It is also easy to implement a
new optimizer in the {\tt ensmallen} framework.  Overall, our goal is to provide
an easy-to-use library that can solve the problem
%\vspace*{-0.4em}
%\begin{equation}
$\operatorname{argmin}_{x} f(x)$
%\end{equation}
%\vspace*{-0.4em}
%\noindent
for any function $f(x)$ that takes a vector or matrix input $x$.
In most cases, $f(x)$ will have special structure; one example might be that
$f(x)$ is differentiable.  Therefore, the abstraction we have designed for {\tt
ensmallen} can optionally take advantage of this structure.  For example, in
addition to $f(x)$, a user can provide an implementation of $f'(x)$, which in
turn allows first-order gradient-based optimizers to be used.  This generally
leads to significant speedups.
%% CS: in the above sentence, it's not clear what is meant by "we must design ..."
%% CS: should it be "we provide ..." or "ensmallen provides ..." ?
%% CS: The overall intent of the sentence is not clear -- to my eyes
%% CS: it doesn't seem to gel well with its surrounding context.

@@

To accomplish the flexibility, {\tt ensmallen} makes heavy use of
C++ template metaprogramming.
When implementing an objective function to be optimized,
a user may only need to implement a few methods; metaprogramming is then automatically
used to check that the given functions match the requirements of the
optimizer that is being used.  When implementing an optimizer, we can assume
that the given function to be optimized meets the required assumptions of the
optimizers, and encode those requirements as compile-time checks
(via \texttt{static\_assert}).

@@

The required API for separable differentiable objective functions (i.e.~those
that would use an optimizer like SGD) is very similar, except that
\texttt{Evaluate()}, \texttt{Gradient()} and \texttt{EvaluateWithGradient()}
should operate only on mini-batches.  The same pattern applies for other
types of objective functions: only a few methods specific to class of objective
function itself must be implemented and then any optimizer may be used.
